### 2023-09-23 spanish/sections/deprecated/training.tex
Create training.tex

\begin{cvhonors}
\cvhonor
{Universidad Católica de Uruguay Winter School in Methods and Data Analysis}
{Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
{Montevideo, URY}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Pontificia Universidad Católica Summer School in Mixed Methods}
{Training in set theory and logic, case studies and multi-methods, process tracing, and experiments in social sciences}
{Santiago, CHL}
{2014}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
{Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
{Montevideo, URY}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Pontificia Universidad Ca\'olica Summer School in Mixed Methods}
{Training in set theory and logic, case studies and multi-methods, process tracing, and experiments in social sciences}
{Santiago, CHL}
{2014}
\end{cvhonors}
